\textbf{Computational Fuzzy Extractors}

### 2013-03-08 trunk/CompFuzzExt.tex
Working on the stronger version of b random claim

\newcommand{\ve}{\vect{e}}
\newcommand{\vm}{\vect{m}}
\newcommand{\vy}{\vect{y}}
\newcommand{\vE}{\vect{E}}
\newcommand{\vS}{\vect{S}}
\newcommand{\vA}{\vect{A}}
\newcommand{\vR}{\vect{R}}
\newcommand{\vU}{\vect{U}}
\newcommand{\vT}{\vect{T}}
\newcommand{\vX}{\vect{X}}
\newcommand{\vB}{\vect{B}}
\newcommand{\vz}{\vect{z}}
\newcommand{\vd}{\vect{d}}
\newcommand{\vs}{\vect{s}}
\newcommand{\vc}{\vect{c}}
\newcommand{\vx}{\vect{x}}
\newcommand{\va}{\vect{a}}
\newcommand{\vb}{\vect{b}}
\newcommand{\vt}{\vect{t}}
\newcommand{\vu}{\vect{u}}
\newcommand{\vF}{\vect{F}}
\newcommand{\recout}{x}
\newcommand{\ignore}[1]{}

@@

It suffices to show that $\D'$ properly prepares a random instance for the distinguisher.  We show this in three claims: 
\begin{enumerate}
\item If $\vA'$ is a random matrix then $\vA$ is a random matrix.
\item If $\vb'$ is uniformly distributed then $\vb$ is uniformly distributed.\bnote{This should be if $\vb' | A$ is uniformly distributed, then $\vb |A $ is uniformly distributed.}
\item If $\vb' = \vA'\vx'+\ve'$ then $\exists \vx$~(uniformly distributed) such that $\vb = \vA \vx + \ve'$ where the last $\alpha$ coordinates of $\ve'$ are $0$ and $\ve_i' = \ve_i$ for $1\leq i\leq m$.
\end{enumerate}
\begin{figure}
\begin{enumerate}
\item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve$.
\item Randomly generate $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$.
\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, where $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.

@@

Before step \ref{step:randomization} the claim is satisfied.  Denote by $\vx'$ the value such that $\vA'\vx'+\ve = \vb$.  
Then define $\vx^*$ as:

@@

x^*_i = \begin{cases}

@@

b_{m-n+i}^*-\sum_{j=1}^n R_{i, j} x_j', & n+1\leq i\leq n+\alpha\,.

@@

Then $\vx^*$ is uniformly random and $\vb^* = \vA^*\vx^* + \ve^*$~(where $\ve^*$ is $\ve'$ with $\alpha$ 0s appended).  Thus, it remains to show that step~\ref{step:randomization} preserves a solution.

@@

For a matrix $\vA$ we will denote the $i$-th row by $\va_i$~(similarly for the matrix formed by $\gamma_{i,j}$).  Thus it suffices to show for all rows $i$, if $b_i^* = \va^*_i \vx^*+e^*_i$  then $b_i = \va_i \vx^* + e^*_i$.

@@

\bnote{We need to justify these steps better.}
\bnote{Is it really standard to go to lower case for the rows?}
We have the following for all $i=1,..., m+\alpha$:

@@

\va_i \vx^* + e_i^* &=\va^*_i\vx^*+\sum_{k=1}^\alpha \gamma_{i} \va^*_{m+k}\vx^*+e_i^*\\
&= \va_i^*\vx^* + e_i^* + \sum_{k=1}^\alpha \mathbf{\gamma}_{i} \va^*_{m+k}\vx^*\\
&= b_i^* + \sum_{k=1}^\alpha\gamma_i \va_{m+k}^* \vx^*\\
&= b_i^* + \sum_{k=1}^\alpha \gamma_i \left(\left( \sum_{j=1}^n \vR_{i, j}x_j^* \right) + x_{n+k}^*\right)\\
&= b_i^* +\sum_{k=1}^\alpha\gamma_i b_{m+k}^*= b_i

@@

If $\D'$ is provided with input distributed as $\vA', \vb'$ where $\vb'$ is uniformly random then $\vb$ is uniformly random.

@@

As before this is clearly satisfied before step~\ref{step:randomization}.  That is, each $b_i^*$ is uniformly and independently random.  After step~\ref{step:randomization} each $b_i$ is a fresh random linear combination of random values:\bnote{We need to better argue this property.}

@@

Thus, each of these values is uniformly and independently random.

%Let $\tilde{\vA} = (\sum_{k=1}^\alpha \gamma_{1, k} \va^*_{m+1}, \ldots, \sum_{k=1}^\alpha \gamma_{1, k} \va^*_{m+1})$ and $\tilde{\vb} = (\sum_{k=1}^\alpha\gamma_{1, k}b^*_{m+1}, \ldots, \sum_{k=1}^\alpha\gamma_{1, k} b^*_{m+\alpha})$. 
%
%The equation above gives us $\vA = \vA' + \tilde{\vA}$ and $\vb = \vA'\vx + \ve + \tilde{\vb}$. Given a uniform $\vu \overset{\$}\leftarrow\Fq^m$ and a $\LWE$ instance $\vA'\cdot \vx + \ve$, the probability that the distinguisher $\D'$ can distinguish a uniform instance from a $\LWE$ instance, when given access to the distinguisher $\D$ is given below:
%\begin{align*}
%&\left|\Pr\left[\D'(\vA', \vu') = 1\right]- \Pr\left[\D'(\vA', \vA'\vx + \ve)=1\right]  \right|\\
%& =\left|\Pr\left[\D(\vA'+ \tilde{\vA}, \vu' + \tilde{\vb})=1\right]- \Pr\left[\D(\vA' + \tilde{\vA}, \vA'\vx + \ve + \tilde{\vb})=1\right]  \right|\\
%&= \left| \Pr\left[\D(\vA, \vu)=1\right]- \Pr\left[\D(\vA, \vA\vx + \ve)=1\right]  \right| \ge \epsilon
%\end{align*}
Together Claims~\ref{cl:randomMatrixDist},~\ref{cl:random ax+e}, and~\ref{clm:random b} show that $\D'$ properly prepares the instance thus, 
\begin{align*}
&\left|\Pr\left[\D'(\vA', \vu') = 1\right]- \Pr\left[\D'(\vA', \vb'=\vA'\vx + \ve)=1\right]  \right|\\
& =\left|\Pr\left[\D(\vA, \vu)=1\right]- \Pr\left[\D(\vA, \vb)=1\right]  \right|\geq \epsilon
\end{align*}
%==========
\ignore{
Before randomized:
$$\vA'\vx' + \ve = \vb'$$
For $i = 1\ldots m$,
$$\sum^{n+\alpha}_{j=1}A_{ij}x_j + e_i = b_i$$
For $i = 1\ldots \alpha$,
$$\sum^{n+\alpha}_{j=1}A_{(m+i)j}x_j = \sum^{n}_{j=1}F_{ij}x_j + x_{n+i} = b_{m+i}$$
}
\end{proof}

>>>>

\newcommand{\ve}{\vect{e}}
\newcommand{\vm}{\vect{m}}
\newcommand{\vy}{\vect{y}}
\newcommand{\vE}{\vect{E}}
\newcommand{\vS}{\vect{S}}
\newcommand{\vA}{\vect{A}}
\newcommand{\vR}{\vect{R}}
\newcommand{\vU}{\vect{U}}
\newcommand{\vT}{\vect{T}}
\newcommand{\vX}{\vect{X}}
\newcommand{\vB}{\vect{B}}
\newcommand{\vz}{\vect{z}}
\newcommand{\vd}{\vect{d}}
\newcommand{\vs}{\vect{s}}
\newcommand{\vc}{\vect{c}}
\newcommand{\vx}{\vect{x}}
\newcommand{\va}{\vect{a}}
\newcommand{\vb}{\vect{b}}
\newcommand{\vgamma}{\mathbf{\Gamma}}
\newcommand{\vt}{\vect{t}}
\newcommand{\vu}{\vect{u}}
\newcommand{\vF}{\vect{F}}
\newcommand{\recout}{x}
\newcommand{\ignore}[1]{}

@@

It suffices to show that $\D'$ properly prepares a random instance for the distinguisher.  We show this in three claims: 
\begin{enumerate}
\item If $\vA'$ is a random matrix then $\vA$ is a random matrix.
\item If $\vb'$ is uniformly distributed conditioned on $\vA'$ then $\vb$ is uniformly distributed conditioned on $\vA$.
%\bnote{This should be if $\vb' | A$ is uniformly distributed, then $\vb |A $ is uniformly distributed.}
\item If $\vb' = \vA'\vx'+\ve'$ then $\exists \vx$~(uniformly distributed) such that $\vb = \vA \vx + \ve'$ where the last $\alpha$ coordinates of $\ve'$ are $0$ and $\ve_i' = \ve_i$ for $1\leq i\leq m$.
\end{enumerate}
\begin{figure}
\begin{enumerate}
\item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve$.
\item Randomly generate $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$.
\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, where $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.\label{step:b generation}

@@

Denote by $\vx'$ the value such that $\vA'\vx'+\ve = \vb$.  
Then define $\vx$ as:

@@

x_i = \begin{cases}

@@

b_{m+i}^*-\sum_{j=1}^n R_{i, j} x_j', & n+1\leq i\leq n+\alpha\,.

@@

We denote by $\vA^*$ the matrix before step~\ref{step:randomization}.  The vector $\vx$ is uniformly random and $\vb^* = \vA^*\vx + \ve$~(where $\ve$ is $\ve'$ with $\alpha$ 0s appended).  Thus, it remains to show that step~\ref{step:randomization} preserves a solution.

@@

For a matrix $\vA$ we will denote the $i$-th row by $\va_i$.  We now show that for all rows $i$, if $b_i^* = \va^*_i \vx+e_i$  then $b_i = \va_i \vx + e_i$.

@@

We have the following for all rows $i$:

@@

\va_i \vx + e_i &= \sum_{j=1}^{n+\alpha} \vA_{ij} x_j + e_i\\
& = \sum_{j=1}^{n+\alpha}\left(\left(\vA^*_{ij}+\sum_{k=1}^\alpha \gamma_{i, k} \vA^*_{(m+k)j}\right)x_j\right) + e_i\\
& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{j=1}^{n+\alpha}\sum_{k=1}^\alpha \gamma_{i, k} \vA^*_{(m+k)j}x_j \\
& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{k=1}^\alpha  \gamma_{i, k} \sum_{j=1}^{n+\alpha} \vA^*_{(m+k)j}x_j\\
& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{k=1}^\alpha \gamma_{i, k} \left(\left( \sum_{j=1}^n \vR_{i, j}x_j^* \right) + x_{n+k}^*\right)\\
& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{k=1}^\alpha\gamma_{i, k} b_{m+k}^*\\
&= b_i^* +\sum_{k=1}^\alpha\gamma_{i,k} b_{m+k}^*= b_i

@@

If $\D'$ is provided with the input distributed as $\vA', \vb'$ where $\vb'$ is uniformly random, then $\vb$ is uniformly random conditioned on $\vA$.

@@

Before step~\ref{step:randomization}, each $b_i^*$ is uniformly and independently random.  After step~\ref{step:randomization}, since the $b_i*$ and $\gamma_i$ are random, then each $b_i$ is a fresh random linear combination of random values:

@@

%We also need to show that $\vb$ is uniformly distributed even conditioned on $\vA$. Step~\ref{step:randomization} randomized each

$\vb$ doesn't dependent on $\vA$ simply because $\vb'$ doesn't dependent on $\vA'$ \xnote{It need show more work on this, maybe?}
Thus, each of these values is uniformly and independently random.
\end{proof}

%Let $\tilde{\vA} = (\sum_{k=1}^\alpha \gamma_{1, k} \va^*_{m+1}, \ldots, \sum_{k=1}^\alpha \gamma_{1, k} \va^*_{m+1})$ and $\tilde{\vb} = (\sum_{k=1}^\alpha\gamma_{1, k}b^*_{m+1}, \ldots, \sum_{k=1}^\alpha\gamma_{1, k} b^*_{m+\alpha})$. 
%
%The equation above gives us $\vA = \vA' + \tilde{\vA}$ and $\vb = \vA'\vx + \ve + \tilde{\vb}$. Given a uniform $\vu \overset{\$}\leftarrow\Fq^m$ and a $\LWE$ instance $\vA'\cdot \vx + \ve$, the probability that the distinguisher $\D'$ can distinguish a uniform instance from a $\LWE$ instance, when given access to the distinguisher $\D$ is given below:
%\begin{align*}
%&\left|\Pr\left[\D'(\vA', \vu') = 1\right]- \Pr\left[\D'(\vA', \vA'\vx + \ve)=1\right]  \right|\\
%& =\left|\Pr\left[\D(\vA'+ \tilde{\vA}, \vu' + \tilde{\vb})=1\right]- \Pr\left[\D(\vA' + \tilde{\vA}, \vA'\vx + \ve + \tilde{\vb})=1\right]  \right|\\
%&= \left| \Pr\left[\D(\vA, \vu)=1\right]- \Pr\left[\D(\vA, \vA\vx + \ve)=1\right]  \right| \ge \epsilon
%\end{align*}

\begin{claim}
If the pair $(\vA', \vb')$ is uniformly distributed, then the pair $(\vA, \vb)$ is uniformly distributed.
\end{claim}
\begin{proof}
Assume that $(\vA', \vb')$ is uniformly distributed.  By \clref{cl:randomMatrixDist}, $\vA$ is uniformly distributed.  Thus, it suffices to show that $\vb | \vA$ is uniformly distributed.  Let $\vb^*$ be the vector generated in step~\ref{step:b generation} and note that $\vb^*$ is uniformly random.  
We show  a stronger claim that $\vb |( \vA, \vA', \vR)$ is uniformly distributed.  Let $\vgamma$ represent the matrix formed by $\gamma_{i,j}$.

 The matrix $\vgamma$ is a deterministic function of $(\vA, \vA', \vR)$.  Thus, $\vb | (\vA, \vA', \vR) \overset{d}= \vb | (\vA, \vA', \vR, \vgamma)$.  The only dependence of $\vb$ on $(\vA, \vA', \vR, \vgamma)$ is in the matrix $\vgamma$.  Thus, $ \vb | (\vA, \vA', \vR, \vgamma) \overset{d}= \vb | \vgamma$. Recall that $\vb = \vb^* +  \left(\begin{array}{c | c}\mathbf{0} &\vgamma\end{array}\right)\vb^*$.  Let $\vT = \vect{I}+  \left(\begin{array}{c | c}\mathbf{0} & \vgamma \end{array}\right)$.  Since $\vT$ is a deterministic function of $\vgamma$, $\vb | \vgamma \overset{d} = \vb | \vT$.

 \bnote{Now we want to say that $\vb$ is uniformly distributed since $\vb'$ is.  If $\vT$ exists we can just that $\vb | \vT = (\vT^{-1} \vb )| \vT = \vb' | \vT = U | \vT$.  It does with very high probability, but I don't want to add this restriction.  Is there a way to get around this problem?}
%\[
%\vA=  \left(\begin{array}{c | c}\vA' & \mathbf{0}\\\hline \vect{R} & \vect{I}\end{array}\right) + \left(\begin{array}{c | c}\mathbf{0} & \mathbf{\Gamma}\end{array}\right) \left(\begin{array}{c | c}\vA' & \mathbf{0}\\\hline \vect{R} & \vect{I}\end{array}\right) 
%\]
%\begin{align*}
%(\vA, \vb) =  \left(\left(\begin{array}{c | c}\vA' & \mathbf{0}\\\hline \vect{R} & \vect{I}\end{array}\right) + \left(\begin{array}{c | c}\mathbf{0} & \mathbf{\Gamma}\end{array}\right) \left(\begin{array}{c | c}\vA' & \mathbf{0}\\\hline \vect{R} & \vect{I}\end{array}\right) \right) , \left(\vb' + \left(\begin{array}{c | c}\mathbf{0} & \mathbf{\Gamma}\end{array}\right) \vb'\right)
%\end{align*}
\end{proof}
\bnote{Remember this isn't good enough.  We need the enhanced claim above.}
Together Claims~\ref{cl:randomMatrixDist},~\ref{cl:random ax+e}, and~\ref{clm:random b} show that $\D'$ properly prepares the instance thus, 
\begin{align*}
&\left|\Pr\left[\D'(\vA', \vu') = 1\right]- \Pr\left[\D'(\vA', \vb'=\vA'\vx + \ve)=1\right]  \right|\\
& =\left|\Pr\left[\D(\vA, \vu)=1\right]- \Pr\left[\D(\vA, \vb)=1\right]  \right|\geq \epsilon
\end{align*}
%==========
\ignore{
Before randomized:
$$\vA'\vx' + \ve = \vb'$$
For $i = 1\ldots m$,
$$\sum^{n+\alpha}_{j=1}A_{ij}x_j + e_i = b_i$$
For $i = 1\ldots \alpha$,
$$\sum^{n+\alpha}_{j=1}A_{(m+i)j}x_j = \sum^{n}_{j=1}F_{ij}x_j + x_{n+i} = b_{m+i}$$
}
\end{proof}
